Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-06-26 snapshot_system/challenge.tex
revise

With these considerations in mind, we study a cluster-based backup service 
with VM-centric deduplication. This service is co-hosted   in the existing set of machines and resource usage is friendly
to the existing applications.  
We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
an architecture and implementation design with deletion support.

>>>>

A deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud without consideration of .
%The traditional approach compares all fingerprints and
%stores one copy for all of a chunk's duplicates.
We call this as  the VM-oblivious (VO) approach.
In designing and selecting a duplication algorithm, we have considered the following options.
\begin{itemize}
\item {\bf Version-based change detection}.
VM snapshots can be  backed up  incrementally by identifying file  blocks that have
changed from the previous version of the snapshot~\cite{Clements2009,Vrable2009,TanIPDPS2011}.
Active snapshots will contain all the information needed to restore the virtual disk
and when deleting a snapshot, data referenced by other snapshots are removed.
While full signature comparison can deliver additional reduction~\cite{Guo2011,Dong,ExtremeBining},
content change detection falls into a VM-centric approach since deduplication is localizable. 
We are seeking for additional optimzations to improve duplication efficency and design the 
assoication of data chunks with the underlying file blocks so that
file block sharing among VMs is minimized.
\item {\bf sampled Index}.
One alternative approach to reducing the use of memory space is 
to use a sampled index with prefetching, proposed  by Guo and Efstathopoulos\cite{Guo2011}. 
An evaluation with our test data shows that using a sampled index can achieve a high
deduplication effiency with a single machine setup.  
One key problem is that the algorithm is VM oblivious and not easy to be adopted for VM-centric.
Another problem is  to design a distributed version 
in deduplicating large bodies of data. 
%The algorithm stores the sampled index in memory, which is required for high
%throughput to avoid the disk-bottleneck problem - since the index itself has no
%locality information, lookups are essentially random, so the index must be
%somehow optimized to prevent excessive disk seeking (the sampling algorithm does
%this by storing the index in memory). 
To use a distributed memory version of the sampled index, every deduplicate request
may access a remote machine for index lookup,  which  incurs a significant overhead.

Another possibiliy is to use this approach partially  in our VM centric solution by indexing
the most popular data chunks. For a small set of popular data chunks, the prefetching strategy
used in the sampled index will not work well because the spatial locality is limited among popular 
data chunks. In our test data,  on average the number of consecutive data chunks is 7, which is too small
to be effective for index sampling.

%To distribute this sampled index, every  each machine would
%either require a complete copy of the index which would have a prohibitive cost in
%memory, or something like memcached must be used, which leaves the same problem
%as the disk bottleneck with every index check potentially using the network.
%The difficulty in storing extremely large bodies of data
%is related, as once 1PB is stored in the system, assuming a sampling rate of 
%1/101 with 22 byte index entires, 55GB of (in memory) index are required.

%Our solution uses more total memory (??how much??), but is more scalable both in
%terms of capactity and distributing the deduplication. The only part of our
%algorithm which requires significant network traffic is the CDS deduplication,
%but this is done after Levels 1 and 2 (dirty bits and comparison to parent), and
%so is only done for a small percent of blocks (?? 5-10\% ??).

\item {\bf Stateless  Data Routing}.
Another approach for duplicate comparison  is to use a content-based hash
partitioning algorithm called stateless data routing~\cite{Dong20??}
that divides the deduplication work with an approximation, which 
is similar to Exreme Binning\cite{extreme_binning09}. 
Again such an approach is VM-oblivious while each request does incur a network routing latency, and then
additional overhead for a bloomer filter based  disk lookup~\cite{Dong20??} or 
a disk index access~\cite{extreme_binning09}.

%We compared our solution to
%content-based hash partitioning by running the algorithm on our set of 
%traces. We used 2MB superchunks and 4KB chunks to partition the data, and use
%the minhashes of the superchunks for routing. The results of this are shown in
%Table~\ref{??}. Routing each chunk to a bin provides good deduplication
%efficiency, and only requires each storage node to keep an index of local data
%and the bin mapping, but misses significant opportunities in our indended use
%case.

%The problem with the Data Routing algorithm is in the very high network traffic.
%Our intended use case is a backup system which runs alongside a number of VMs,
%in order to save costs. Data Routing makes no use of the inherent locality in
%such a system, and therefore puts a much higher network burden on machines which
%are also running 35 VMs each. This will reduce the available network bandwidth
%to users of the VMs, and/or reduce the possible deduplication throughput.
\end{itemize}

With these considerations in mind, we study a 
VM-centric appraoch (called VC)
for a backup service co-hosted   in the existing set of machines and resource usage is friendly
to the existing applications.  
We will first discuss and analyze the integration of the VM-centric deduplication strategies with fault isolation, and then present
an architecture and implementation design with deletion support.

### 2013-06-26 snapshot_system/snapshot.tex
revise

A deduplication scheme compares the fingerprints of the current snapshot
with its parent snapshot and also other snapshots in the entire cloud.
The traditional approach compares all fingerprints and 
stores one copy for all of a chunk's duplicates.
We call this as  the VM-oblivious (VO) approach.
In comparison, we analyze the design of
a VM-centric approach (VC) which differentiates duplicates within a VM and cross VMs,
and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.

\subsection{Inner and cross VM deduplication}

Inner-VM duplication can be very effective within VM's snapshots. There
are typically a large number of duplicates existing among the snapshots
for a single VM.  Localizing the snapshot data deduplication within a VM
improves the system by:
increasing data independence between different VM backups,
simplifying snapshot management and statistics collection,
and facilitating parallel execution of snapshot operations.
On the other hand, cross-VM duplication can also be desirable mainly due to widely-used software and libraries. 
As the result, different VMs tend to backup large amount of highly similar data.
We integrate those strategies together as follows.
%Our multi-level pipeline process can minimize 
%the cost of deduplication while maximize the its efficiency at each level,
%and it is parallel since each segment is processed independently.

\begin{itemize}
\item \textbf{Dirtybit-based coarse-grain inner-VM deduplication.}
The first-level deduplication is to follow the standard dirty bit approach, but is conducted
in the coarse grain segment level.
We use the  Xen virtual device driver which supports a feature called "changed block tracking''
for the storage device
and the dirty bit setting is maintained in a coarse grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment  size.

It should be noted that dirtybit tracking is supported or can be easily implemented in many 
major virtualization solution vendors. 
%(VMware, Xen, Microsoft).  
VMware support it directly; the VMWare hypervisor has an API to let external backup application know 
the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
We implement dirty bit tracking this way in Alibaba's platform.  
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic, therefore changed block tracking can be implemented externally.

\item \textbf{Chunk-level fine-grain inner-VM detection.}
The best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??}. This allows the system to
achieve deduplication even when there are insertions/deletions which would
affect many fixed-size chunks.
Thus the second-level inner-VM deduplication is to perform this chunking for
dirty segments, and to compare the snapshot with its parent. 
We load the chunk fingerprints in the corresponding segment from the
parent and perform fingerprint matching for further inner-VM deduplication.
The amount of memory for maintaining those fingerprints  is small, as we only
load one segment at a time.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

\item \textbf{Cross-VM deduplication.}
This step accomplishes the standard global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the most popular items. 
%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
\end{itemize}

>>>>

%A deduplication scheme compares the fingerprints of the current snapshot
%with its parent snapshot and also other snapshots in the entire cloud.
%The traditional approach compares all fingerprints and 
%stores one copy for all of a chunk's duplicates.
%We call this as  the VM-oblivious (VO) approach.
Our VC design has the following objectives:
\begin{itemize}

\item
1) Localize the deduplication and data blocking within each VM as much as possible so 
that any failure of a file system block mainly affects the associated VM.
Localizing the snapshot data deduplication within a VM
improves the system by increasing data independence between different VM backups,
simplifying snapshot management and statistics collection,
and facilitating parallel execution of snapshot operations.
\item
2) Maintain a competitive deduplication effiency while being resource-friendly to other
existing cloud services.
Cross-VM duplication can be desirable since  there are many cloud images
use widely-used software and libraries and their data blocks are duplicate. 
As the result, different VMs tend to backup large amount of highly similar data.
\item
3)  Mininimize the number of data chunks shared among VMs and add extra replicas to incrase
fault resilience for such data chunks.
\end{itemize}

\subsection{Key VC Strategies}

%Inner-VM duplication can be very effective within VM's snapshots. There
%are typically a large number of duplicates existing among the snapshots
%for a single VM.

%Our multi-level pipeline process can minimize 
%the cost of deduplication while maximize the its efficiency at each level,
%and it is parallel since each segment is processed independently.

%Our VC differentiates duplicates within a VM and cross VMs,
%and conducts \textit{Inner-VM} and \textit{cross-VM} detection separately.

\begin{itemize}
\item \textbf{Local duplicate search.}
We start with the standard dirty bit approach in a coarse grain segment level
and use the  Xen virtual device driver to implement a feature called ``changed block tracking''
for the storage device and the dirty bit setting is maintained in a coarse grain level we call it a segment.
In our implementation, the segment size is 2MB. 
Since every write for a segment will touch a dirty bit, the device driver maintains dirty bits in memory
and cannot afford a small segment  size.

It should be noted that dirtybit tracking is supported or can be easily implemented in many 
major virtualization solution vendors. 
%(VMware, Xen, Microsoft).  
%VMware support it directly; 
The VMWare hypervisor has an API to let external backup application know 
the changed areas since last backup. Xen doesn't directly support it, However, their open-source 
architecture allows anyone to extend the device driver, thus enabling changed block tracking. 
We implement dirty bit tracking this way in Alibaba's platform.  
The Microsoft SDK provides an API that allows external applications to monitor 
the VM's I/O traffic, therefore changed block tracking can be implemented externally.

Since the best deduplication uses a nonuniform chunk size 
in the average of 4K or 8K~\cite{??},  
%This allows the system to achieve deduplication even when there are insertions/deletions which would
%affect many fixed-size chunks.
we conduct additional local inner-VM deduplication by comparing
chunk signatures within a dirty segment from its parent snapshot. 
We load the chunk fingerprints in the corresponding segment from the
parent and perform fingerprint matching for further inner-VM deduplication.
The amount of memory for maintaining those fingerprints  is small, as we only
load one segment at a time.
For example, with a 2MB segment, there are about 500 fingerprints to compare.

@@

\item \textbf{Cross-VM deduplication with top $k$ popular chunks}
This step accomplishes the standard global fingerprint  comparison as conducted
in the previous work~\cite{??}.
One key observation is that the inner deduplication has removed many of the duplicates.
There are fewer deduplication opportunities across VMs while the memory and network
consumption for global comparison is more expensive.
Thus our approximation is that the global fingerprint comparison only searches for the most popular items. 
%Since duplicate sharing patterns among  VM follows a zip-like distribution,  
\end{itemize}
